Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-20 paper.qmd
Updated the function name

error_plot_two_curvy <-
  plot_mse(error_two_curvy) +
  scale_x_continuous(breaks =
    sort(unique(error_two_curvy$a1))[
      seq(1, length(
        unique(error_two_curvy$a1)), 
        by = 5)]) +
  scale_color_manual(
    values=c('#e41a1c','#ff7f00','#4daf4a', 
             "#a65628",'#636363', '#984ea3')) +
  theme(aspect.ratio = 1.5)
```

@@

error_plot_pbmc <- plot_mse(error_pbmc) +
  scale_x_continuous(breaks = sort(unique(error_pbmc$a1))[c(1, 5, 9, 13, 17, 21, 26)]) +
  scale_color_manual(values=c('#999999','#a65628','#e41a1c','#377eb8','#4daf4a','#ff7f00','#984ea3','#f781bf'))

@@

error_plot_mnist <- plot_mse(error_mnist) +
  scale_x_continuous(breaks = sort(
    unique(error_mnist$a1))[append(seq(1, length(unique(error_mnist$a1)), 
                                       by = 5), 24)]) +
  scale_color_manual(
    values=c('#a65628', '#984ea3', '#999999', 
             '#377eb8', '#ff7f00', '#e41a1c')) +
  theme(aspect.ratio=1.5)

>>>>

error_plot_two_curvy <-
  plot_rmse(error_two_curvy) +
  scale_x_continuous(breaks =
    sort(unique(error_two_curvy$a1))[
      seq(1, length(
        unique(error_two_curvy$a1)), 
        by = 5)]) +
  scale_color_manual(
    values=c('#e41a1c','#ff7f00','#4daf4a', 
             "#a65628",'#636363', '#984ea3')) +
  theme(aspect.ratio = 1.5)
```

@@

error_plot_pbmc <- plot_rmse(error_pbmc) +
  scale_x_continuous(breaks = sort(unique(error_pbmc$a1))[c(1, 5, 9, 13, 17, 21, 26)]) +
  scale_color_manual(values=c('#999999','#a65628','#e41a1c','#377eb8','#4daf4a','#ff7f00','#984ea3','#f781bf'))

@@

error_plot_mnist <- plot_rmse(error_mnist) +
  scale_x_continuous(breaks = sort(
    unique(error_mnist$a1))[append(seq(1, length(unique(error_mnist$a1)), 
                                       by = 5), 24)]) +
  scale_color_manual(
    values=c('#a65628', '#984ea3', '#999999', 
             '#377eb8', '#ff7f00', '#e41a1c')) +
  theme(aspect.ratio=1.5)
